later

### 2023-06-16 CPP_paper/paper.tex
cleaned up tex file

\item When viewing $K_v$ as the completion of $K$, its \texttt{valued} instance comes from the completion of the valuation on $K$, and this is of course different from the \texttt{valued} instance on the fraction field of $R_v$, itself isomorphic to $K_v$, that instead comes from the \texttt{discrete_valuation_ring} instance on $R_v$.

@@

@@

insert here the iso between Laurent series and the completion

@@

\section{Discussion}

@@

\item Future work (not too much, but towards LCFT)
\item Related works

@@

\subsection{Implementation Details}
\item bundled vs unbundled \texttt{uniformizer}'s and the choice of having them in K or in R or in R.int\dots
\item insert here the "double" $Q_p$.
\item the loop forcing the instance \texttt{discretely\_normed\_field} to be only a local one
\item [MAY BE] Discuss working in $\ZZ_{m0}$ vs in $\RR$ for the DVR\_extension
\item The instance of \path{valued} at the end of basic is defined on THE fraction ring and not on A fraction field because otherwise this would get into a diamond. Look at the examples in \path{extension}. Observe that \path{height_one_spectrum.valued_adic_completion K v} takes as argument $K$ (that is A fraction ring of $R$), whereas \path{discrete_valuation.with_zero.valued} takes as argument a DVR (in this case, $R_v$). Since the completion at $v$ of the fraction ring $frac R$ is not equal to $K_v$, this lead to no problem.
%\section*{Acknowledgement}--LATER (fundings?)
\end{document}

>>>>

\item When viewing $K_v$ as the completion of $K$, its \texttt{valued} instance comes from the completion of the valuation on $K$, and this is of course different from the \texttt{valued} instance on the fraction field of $R_v$, itself isomorphic to $K_v$, that instead comes from the \path{discrete_valuation_ring} instance on $R_v$.

@@

Give our definition and the claims that \mi{TODO : finite extensions of $\laurentseries$ and of $\QQ_p$ are local fields.}

@@

\item Unlike the $p$-adic, the completion of the ring of rational functions had not yet been defined in mathlib.
\item Put both a valuation and a norm on $\laurentseries$
\item iso between Laurent series and the completion
\item Definition of Eq char local field
\item Our definition of ring of integers is the integral closure of $\powerseries$ in $K$, mainly to adapt to what has been done for number fields.
\item The definition \path{ring_of_integers_algebra}
\item $\laurentseries$ is an eq. char. local ring \fil{(and also $\laurentseries[{\FF[q]}]$?)}

@@

@@

\item Definition of Mixed char local field
\item Our definition of ring of integers is the integral closure of $\ZZ_p$ in $K$, mainly to adapt to what has been done for number fields.
\item The definition \path{ring_of_integers_algebra}, "equal" to the one for eq. char. local fields
\item The proof that a $\QQ_p$ is a mixed char local field.
\item Discussion about the two $\QQ_p$'s from a mathematical point of view.
\item Say that most of the techniques used for the iso about Laurent series adapted to \path{padic_ring_equiv} IF TRUE
\item A proof that the ring of integers is a DVR (once $\ZZ_p$ becomes the right $\ZZ_p$ --- so, not only a DVR, which it is, but the \path{valuation_subring} of $\QQ_p$ --- this will follow from the general results about DVR's).

@@

\section{Discussion}
\begin{itemize}
\item Future work (not too much, but towards LCFT)
\item Related works
\end{itemize}
\subsection{Implementation Details}
\begin{itemize}
\item bundled vs unbundled \texttt{uniformizer}'s and the choice of having them in K or in R or in R.int\dots
\item insert here the "double" $Q_p$ in particular the fact we found a \path{metric} instance on $\QQ$.
\item the loop forcing the instance \texttt{discretely\_normed\_field} to be only a local one
\item [MAY BE] Discuss working in $\ZZ_{m0}$ vs in $\RR$ for the DVR\_extension
\item The instance of \path{valued} at the end of basic is defined on THE fraction ring and not on A fraction field because otherwise this would get into a diamond. Look at the examples in \path{extension}. Observe that \path{height_one_spectrum.valued_adic_completion K v} takes as argument $K$ (that is A fraction ring of $R$), whereas \path{discrete_valuation.with_zero.valued} takes as argument a DVR (in this case, $R_v$). Since the completion at $v$ of the fraction ring $frac R$ is not equal to $K_v$, this leads to no problem.
\end{itemize}
%\section*{Acknowledgement}--LATER (fundings?)
\end{document}
